On Secure Delegation of SampBQP with a Classical Client

### 2020-01-22 blind.tex
Change "private" to "blind"
Clarify how decryption commutes with measurement

\section{Private Delegation}

@@

First we give a definition of CPA security for delegation schemes... TODO

\begin{dfn}
	A $\QPIP_\tau$ protocol is IND-CPA secure if, for any polynomial time prover $\cA$,
	$$\abs{\Pr[\cA]}$$
	where $x$ is the input of the verifier.
\end{dfn}

\subsection{Quantum homomorphic encryption scheme}

@@

We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}. We use this particular QFHE because it allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item $\mathsf{QHE.Dec}$ ``commutes" with measurements. \Ethan{Need to elaborate just a bit more here; i.e. need to mention X/Z only} If the ciphertext is a measurement result, it can also be done classically.
\end{itemize}

>>>>

\section{Constant-Round, Blind, and Verifiable Delegation}

@@

We now present a constant-round, blind, and verifiable delegation scheme for $\SampBQP$ as an application of our $\QPIP_0$ construction for $\SampBQP$,
which we achieve by using the homomorphic encryption scheme from \cite{mahadev_qfhe} together with our construction.

\subsection{Homomorphic Encryption with Classical Client}

@@

We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{itemize}
